---
title: "P8105_hw5"
author: "Zhezheng Jin"
date: "2023-11-10"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(knitr)
library(janitor)

opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1

#### Data import
```{r}
homicide <- read_csv("./data_file/homicide-data.csv")
view(homicide)
```
Description: 

This dataset has `r nrow(homicide)` observations and `r ncol(homicide)` variables.
There are `r nrow(homicide)` number of observations of homicide cases in the 50 large U.S. cities and `r ncol(homicide)`  variables, including `r names(homicide)`. 

#### Homicides within cities
```{r}
homicide <-homicide %>%
  mutate(
    city_state = paste(city, state, sep=", "),
    unsolved = disposition %in% c("Closed without arrest", "Open/No arrest")
    ) %>%
  filter(city_state != "Tulsa, AL")

cities_sum <- homicide %>%
  group_by(city_state) %>%
  summarise(
    total_homicides = n(),
    unsolved_homicides = sum(unsolved, na.rm = TRUE)
  )

cities_sum
```

#### Baltimore summary
```{r}
baltimore_sum <-  
  cities_sum %>%
  filter(city_state == "Baltimore, MD")
baltimore_test <-
  prop.test(
  x = baltimore_sum %>% pull(unsolved_homicides),
  n = baltimore_sum %>% pull(total_homicides)
  ) %>%
  broom::tidy()

baltimore_test
```

#### Summary of each city
```{r}
prop_test_city <- function(unsolved, total) {
    test_result <- prop.test(x = unsolved, n = total)
    return(test_result)
    }

cities_proportion <- cities_sum %>%
  mutate(
    prop_test_result = map2(unsolved_homicides, total_homicides, prop_test_city),
    tidy_results = map(prop_test_result, broom::tidy)
  ) %>%
  select(city_state, tidy_results) %>%
  unnest(tidy_results) %>%
  select(city_state, estimate, conf.low, conf.high)

cities_proportion
```


#### Plot: Estimated proportion of unsolved homicides & CIs by city
```{r}
cities_proportion %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>%
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

## Problem 2



